The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-08-24 JStatSoft_forestinventory_master-concordance.tex
update Andreas 24.08.2017

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 123 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 131:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 227:%
139 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 262:%
1 78 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 341:%
175 13 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Onephase_Estimators and their Application.Rnw:ofs 355:%
1 25 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 381:%
190}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 382:%
1 124 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 911:%
192}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 912:%
1 118 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 179 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1302:%
194 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1313:%
1 13 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1327:%
206 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1336:%
1 21 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1358:%
216 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1374:%
1 20 1 1 4 6 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1629:%
233 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1633:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1638:%
238 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 123 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 131:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 227:%
139 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 262:%
1 77 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 340:%
175 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 356:%
1 125 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 886:%
192}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 887:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1406:%
194 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1417:%
1 54 1 1 2 11 0 1 2 32 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1517:%
206 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1526:%
1 21 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1548:%
216 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1564:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1822:%
233 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1826:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1831:%
238 11 1}

### 2017-08-24 rnw/Analysis and Visualization.Rnw
update Andreas 24.08.2017

If we want to compare the results and performance of different estimation methods and estimators for a given global or small area inventory data set, the function to start with is \code{estTable()}. This function restructures the results of \code{onephase}, \code{twophase} and \code{threephase} estimations and merges them into one single data set that provides the basis for further analysis. For demonstration purposes, we will first recalculate the one-phase estimations as well as the two-phase and three-phase \textit{extended pseudo synthetic} and the \textit{pseudo synthetic} estimations for the \code{grisons} dataset:

@@

\begin{small}
<<>>=
extpsynth_3p<- threephase(formula.s0 = tvol ~ mean,
                formula.s1 = tvol ~ mean + stddev + max + q75, data = grisons,
                phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
                small_area=list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
                                unbiased = TRUE))
@
\end{small}

\begin{small}
<<>>=
psynth_3p<- threephase(formula.s0 = tvol ~ mean,
                formula.s1 = tvol ~ mean + stddev + max + q75, data = grisons,
                phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
                small_area = list(sa.col = "smallarea", 
                                  areas = c("A", "B", "C", "D"),
                                  unbiased = FALSE))
@
\end{small}

>>>>

If we want to compare the results and performance of different estimation methods and estimators for a given global or small area inventory data set, the function to start with is \code{estTable()}. This function restructures the results of \code{onephase()}, \code{twophase()} and \code{threephase()} estimations and merges them into one single data set that provides the basis for further analysis. For demonstration purposes, we will first recalculate the one-phase estimations as well as the two-phase and three-phase \textit{extended pseudo synthetic} and the \textit{pseudo synthetic} estimations for the \code{grisons} dataset:

@@

\begin{small}
<<>>=
extpsynth_3p<- threephase(formula.s0 = tvol ~ mean,
                formula.s1 = tvol ~ mean + stddev + max + q75, data = grisons,
                phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
                small_area=list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
                                unbiased = TRUE),
                boundary_weights = "boundary_weights")
@
\end{small}

\begin{small}
<<>>=
psynth_3p<- threephase(formula.s0 = tvol ~ mean,
                formula.s1 = tvol ~ mean + stddev + max + q75, data = grisons,
                phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
                small_area = list(sa.col = "smallarea", 
                                  areas = c("A", "B", "C", "D"),
                                  unbiased = FALSE),
                boundary_weights = "boundary_weights")
@
\end{small}

### 2017-08-24 rnw/Calculation of Confidence Intervals.Rnw
update Andreas 24.08.2017

>>>>

% NOTE:
% - Provide all confidence equations for the estimators: onephase, twophase, threephase
% - Give recommendations for n-threshold of unbiased estimators based on confid.level (dfs)
% - ... and asymptotic of estimators
% - Interpretation of Confidence Intervals
%

The estimated variance provides a measure of uncertainty for a given point estimate.

Confidence intervals thus allow for a much more intuitive interpretation of the uncertainties associated to a point estimate, and are also more suited to be incorporated into planning forest management operations.

% Frequentisitsche Interpretation streng genommen die einzig richtige: unter rein hypothetischer Wiederholung der Inventur (Gleicher Schaetzer, gleicher Wald, gleiche Hilfvariablen / Aux.info) werden 95\% der berechneten Intervalle den wahren Wert enthalten. Man weiss nun aber - selbst wenn man das machen wuerde (was praktisch ja nie der Fall sein wird) - nie, auf welche der berechneten Intervalle das zutreffen wird. Die klassische statistische Interpration ist hier also nicht zulaessig (ungleich: der wahre wert befindet sich mit 95\% Sicherheit in meinem berechneten Intervall).
% 
% Da diese strenge Interpretation dem Praktiker nicht viel nuetzen wird (ausser evtl einem Gefuhl der Sicherheit), kann man sich aufgrund der CI-Breite (abhaengig von der Varianz der SChaetzung) an folgender Frage orientieren: "Wuerde ich innerhalb des Vertrauensintervalles zu der selben Entscheidung (z.b. Eingriff ja/nein, Vorrat um x\% reduzieren) kommen, oder nicht?" Wenn ja, dann ist die Genauigkeit der SChaetzung bereits ausreichend, wenn nein, dann ist dies die Motivation nach effizien
% Stichwort: signifikanz vs. relevanz

The confidence intervals for one-phase as well as two-phase and three-phase global and small area point estimates are defined by

\textit{One-Phase Estimation}

\begin{equation}\label{ci_1phase}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})},
                              \hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})}\bigg{\rbrack}
\end{equation}

% ------------------------------------------ %
\textit{Two-Phase and Three-Phase Global Estimation}

\begin{equation}\label{ci_2phase_global}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})},
                              \hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})}\bigg{\rbrack}
\end{equation}

% ------------------------------------------ %
\textit{Two-Phase and Three-Phase Small Area Estimation}

\begin{equation}\label{ci_2phase_sae}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})},
                              \hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\var(\hat{Y})}\bigg{\rbrack}
\end{equation}

where $\hat{Y}$ is the respective point estimate, $\var(\hat{Y})$ is the respective estimated variance, and $1-\alpha$ is the confidence level. Note that in the three-phase case, $p$ is the number of parameters used in the \textit{full} regression model. In case of cluster-sampling, $n_{2,G}$ is the number of terrestrial clusters (a cluster constitutes the sample unit and comprises multiple sample plots).

In the package \pkg{forestinventory}, the confidence levels for all estimation methods and estimators can be computed by the S3 generic function \code{confint()}. The function requires an estimation object created by the \code{onephase()}, \code{twophase()} or \code{threephase()} function. Optionally, the confidence level $1-\alpha$ can be specified by the argument \code{level} and has a default value of 0.95, which will cause the function to return the 95\% confidence intervall.

The 95\% confidence intervall for the small area estimations by the \textit{extpsynth} estimator (section \ref{sec:twophase_sae}) can for example be applied by:

\begin{small}
<<>>=
confint(extpsynth_2p)
@
\end{small}

### 2017-08-24 rnw/Threephase_Estimators and their Application.Rnw
update Andreas 23.08.2017
update Andreas 24.08.2017

We first recalculate the regression coefficients $\hat{\pmb{\gamma}}_{s_2}$ and $\hat{\pmb{\theta}}_{s_2}$, and their variance-covarianve matrices $\hat{\pmb{\Sigma}}_{\hat{\pmb{\gamma}}_{s_2}}$ and $\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}$ as

@@

>>>>

We first recalculate the regression coefficients $\hat{\pmb{\gamma}}_{s_2}$ and $\hat{\pmb{\theta}}_{s_2}$, and their variance-covarianve matrices $\hat{\pmb{\Sigma}}_{\hat{\pmb{\gamma}}_{s_2}}$ and $\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{s_2}}$ under the extended auxiliary vector as

@@

<<echo=FALSE>>=
options(width=90) 
@

### 2017-08-24 rnw/Twophase_Estimators and their Application.Rnw
update Andreas 24.08.2017

% ---------------------------------------------------------------------------- %
\subsection{Global Estimators}

@@

\begin{itemize}
  \itemsep0em
  \item the regression model (\code{formula}) as specified in the \code{lm}-function \citep{R}
  \item the \code{data.frame} containing the inventory information (\code{data})
  \item the \code{list}-object \code{phase_id} taking the column name (\code{phase.col}) specifying the sample association of an observation ($s_1$ or $s_2$) and the indicator for the $s_2$ (\code{terrgrid.id})
  \item the name of the column containing the weights $w(x)$ of the boundary adjustments (optional)
\end{itemize}

@@

\begin{subequations}\label{eq:ext_varexternal_2p_extsynth}
\begin{align}
  \hat{\var}_{ext}(\hat{Y}_{G,extsynth,2p}) & = \frac{1}{n_{2,G}} \frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(\hat{R}(x)-\bar{\hat{R}})^2 \label{eq:ext_varexternal_2p_extsynth} \\
  \hat{\var}_{ext}(\hat{Y}_{G,extpsynth,2p}) & =
 \frac{1}{n_{1,G}}\frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(Y(x)-\bar{Y}_{2,G})^2 \nonumber \\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(\hat{R}(x)-\bar{\hat{R}})^2 \label{eq:ext_varexternal_2p_extpsynth}
\end{align}
\end{subequations}

>>>>

% ---------------------------------------------------------------------------- %
\subsection{Global Estimators}
\label{sec:twophase_globest}

@@

\begin{itemize}
  \itemsep0em
  \item the regression model (\code{formula}) as specified in the \code{lm}-function \citep{R}
  \item the \code{data.frame} containing the inventory information (\code{data})
  \item the \code{list}-object \code{phase_id} taking the column name (\code{phase.col}) specifying the sample association of an observation ($s_1$ or $s_2$) and the indicator for the $s_2$ phase (\code{terrgrid.id})
  \item the name of the column containing the weights $w(x)$ of the boundary adjustments (optional)
\end{itemize}

@@

\begin{subequations}\label{eq:ext_varexternal_2p_extsynth}
\begin{align}
  \hat{\var}_{ext}(\hat{Y}_{G,extsynth,2p}) & = \frac{1}{n_{2,G}} \frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(\hat{\mathbb{R}}(x)-\bar{\hat{\mathbb{R}}})^2 \label{eq:ext_varexternal_2p_extsynth} \\
  \hat{\var}_{ext}(\hat{Y}_{G,extpsynth,2p}) & =
 \frac{1}{n_{1,G}}\frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(Y(x)-\bar{Y}_{2,G})^2 \nonumber \\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\frac{1}{n_{2,G}-1}\sum_{x\in{s_{2,G}}}(\hat{\mathbb{R}}(x)-\bar{\hat{\mathbb{R}}})^2 \label{eq:ext_varexternal_2p_extpsynth}
\end{align}
\end{subequations}
